Bayesian Evidence Synthesis:opioid crisis

### 2020-03-11 latex/newpaper.tex
histogram generated

\normalsize 
There exist two data sets; survey data ($n_A, x_A$), and ambulance attended overdose data ($U_t$). The two data sets are simulated as follows. 
The true value of $p_A$ was set as $p_A=0.8$ for the survey data. [n_A? the setup described here above has a single x ]
It is assumed that the data was collected for a year (t=1,2,3, ..., 12) and 
$x_t$ values were independentally generated from the Binomial distribution (\ref{ambulance}).  In terms of overdose data, It is assumed that the true values of parameters for overdose model were $\mu=\log0.05,\ \sigma=1$.
The vector of $O_t$ was generated following the overdose model (\ref{overdose}). The vector of $U_t$ was generated from the Binomial relation of the two variables ($\ref{over_amb}$). The two generated vectors have the same length with the survey data (t=1,2,3, ..., 12).  Note that only $U_t$ and $x_t$ are known as the likelihood and $p_A$ needs to be estimated first so as to estimate $O_t$ which is the ultimate interest of the research.\\

@@

The result from the simple case scenario is illustrated below.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/earlyresult1_ot.png}
	\caption{Boxplot of posterior samples of $O_t$ (2000 samples for each month) with actual data points of simulated $O_t$ values. The simulated values are shown as red dots.}
	\label{pst_ot}
\end{figure}

>>>>

\normalsize 
There exist two data sets; survey data ($n_A, x_A$), and ambulance attended overdose data ($U_t$). The two data sets were simulated as follows. 
It was assumed that the two data sets were collected for a year (t=1,2,3, ..., 12). The true value of $p_A$ was set as $p_A=0.8$ and the survey sample size $n_A$ was set as $n_A=1000$ for every months. The $x_A$ values for each month were independentally generated from the Binomial distribution (\ref{ambulance}).  In terms of the overdose data, It is assumed that the true values of parameters for overdose model were $\mu=\log0.05,\ \sigma=1$.
The vector of $O_t$ was generated following the overdose model (\ref{overdose}). The vector of $U_t$ was generated from the Binomial relation of the two variables ($\ref{over_amb}$). The two generated vectors have the same length with the survey data (t=1,2,3, ..., 12).  Note that only $U_t$ and $x_A$ are known as the likelihood and $p_A$ needs to be estimated first in order to estimate $O_t$ which is the ultimate interest of the research.\\

@@

The result from the simple case scenario is illustrated below. Markov chain Monte Carlo packege PYMC3 3.8\cite{pymc3} was used  with Python 3.7 for the simulation. Figures were generated by Python 3.7. The results were verified with JAGS 4.3.0 and R 3.6.2.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/earlyresult1_ot.png}
	\caption{Boxplot of posterior samples of $O_t$ (2000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot}
\end{figure}
